\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-28 OaklandSubmission/impl.tex
minor
pipe impl

\section{Implementation}
\label{sec:impl}
We discuss some  implementation details of \tool.
The  \tool compiler is written in Python and
compiles each of our benchmarks in under a second to C++ code that
makes calls to the ABY
library~\cite{aby}. We use the default ABY configuration for our
experiment \footnote{We set the security parameter to 128 and use OT
extension-based arithmetic multiplication triples generation.}. ABY
provides multi-threading support (for the offline phase of the \mpc
protocol); we leverage the support and use at most four threads in our
evaluation.

Our current implementation supports the following operators:
addition, subtraction, multiplication, division by powers of two, left
shift,
logical and arithmetic right shifts, bitwise-(and, or, xor), unary
negation, 
bitwise-negation, logical-(not, and, or, xor), and comparisons (less
than, greater than, equality). 
Because of their high cost, integral division and floating-point
operators are not supported natively by \tool. 
However, we have implemented integral division in 30 lines of \tool,
while the floating-point support in ABY is under active
development~\cite{ddkssz15}.

Some of our benchamrks require accessing arrays at secret
indices. While \tool enforces the array indices to be
public, secret indices can be encoded in \tool using multiplexers.
For example, consider the expression $A[x]$ where $A$ is an array of
size 2 and $x$ is secret-shared. The developer can expresse
this functionality in \tool as $\cond{x > 0}{A[1]}{A[0]}$. In general,
a secret access to an array of
size $2^n$ requires $2^{n}-1$ multiplexers in \tool.

>>>>

\section{Implementation}
\label{sec:impl}
We discuss some  implementation details of \tool.
The  \tool compiler is written in Python and
compiles each of our benchmarks in under a second to C++ code that
makes calls to the ABY
library~\cite{aby}. 
ABY provides a GMW-based~\cite{gmw} and a  Yao-based~\cite{yao} protocol for boolean computations.
Although \tool can generate code for both, we have observed better performance when using the latter
and use it in our evaluation.
We use the default ABY configuration for our
experiment \footnote{We set the security parameter to 128 and use OT
extension-based arithmetic multiplication triples generation.}. ABY
provides multi-threading support (for the offline phase of the \mpc
protocol); we leverage the support and use at most four threads in our
evaluation.

\tool programs can have the following operators:
addition, subtraction, multiplication, division by powers of two, left
shift,
logical and arithmetic right shifts, bitwise-(and, or, xor), unary
negation, 
bitwise-negation, logical-(not, and, or, xor), and comparisons (less
than, greater than, equality). 
Because of their high cost, integral division and floating-point
operators are not supported natively by \tool. 
However, we have implemented integral division in 30 lines of \tool,
while the floating-point support in ABY is under active
development~\cite{ddkssz15}.

Some of our benchmarks require accessing arrays at secret
indices. While \tool enforces the array indices to be
public, secret indices can be encoded in \tool using multiplexers.
For example, consider the expression $A[x]$ where $A$ is an array of
size 2 and $x$ is secret-shared. The developer can express
this functionality in \tool as $\cond{x > 0}{A[1]}{A[0]}$. In general,
a secret access to an array of
size $n$ requires ${n}-1$ multiplexers in \tool.

### 2017-10-28 OaklandSubmission/pipe.tex
pipe impl

We  describe ``secure code partitioning'' that allows us to execute {\it large} programs, i.e., programs with a large number of operations.
In more detail, let $P$ be a program in our source language that generates a circuit $\crct$. For a large enough $P$, the circuit $\crct$  can be larger than the memory size\footnote{In fact, there is an upper limit of $2^{32}-1$ gates for the circuit size in ABY but for most machines the memory limit is hit first} and fail to execute. Partitioning enables us to
execute such programs via a source to source transformation that is oblivious to the underlying \mpc backend. Partitioning decomposes the program $P$ into a sequence of smaller \tool programs $Q_1||Q_2||\cdots||Q_k$ (defined below). We compile and execute each $Q_i$ sequentially, feeding the outputs of $Q_i$ as state information to $Q_{i+1}$. We prove that partioning is correct ($P$ and $Q_1||Q_2||\cdots||Q_k$ compute the same functionality) and secure (execution of $Q_1||Q_2||\cdots||Q_k$ does not reveal any more information than $P$). More details follow.

Let $P$ be a program that takes (secret) inputs $x$ and $y$ and produces an output $z$ to both parties (Alice and Bob). Let $P_1||P_2||\cdots||P_k$ be a sequence of programs such that the following holds: Define $s_0 = \bot$ (the public empty state). For all $1\leq i\leq k-1$, $P_i$ takes inputs $x, y$ and $s_{i-1}$ and outputs  state information $s_i$. Finally, $P_k$ takes inputs $x,y$ and $s_{k-1}$ to  output $z$. Each program $P_i$ ($1\leq i\leq k$) is required to be ``sufficiently'' small (as described later). It is possible to decompose any program $P$  into such $P_1||P_2||\cdots||P_k$. If \tool generates circuit $\crct_i$ from $P_i$, the parties can execute $\crct_1||\crct_2||\cdots||\crct_k$ sequentially (in a distributed setting)  to obtain $s_1,\cdots,s_{k-1},$ and finally output $z$. At the $i^{\textrm{\tiny{th}}}$ step, the parties only need to store information proportional to $x,y,s_{i-1}$ and $\crct_i$ (which is much smaller than $\crct$). However, this execution enables the parties to learn $s_i$ (for all $1\leq i\leq k-1$), which completely breaks the security.

To overcome this problem, we define a sequence of new programs $Q_i$ ($1\leq i\leq k$) as follows. Once again, define $s_0 = \bot$. Without loss of generality, let all $s_i$ be values in some additive ring $(\mathbb{Z},+)$ (e.g., the additive ring $(\mathbb{Z}_{2^{64}},+)$ i.e., the additive ring of integers modulo $2^{64}$). 
Let $r_1,\cdots,r_{k-1}$ be a sequence of random values sampled from the same ring $(\mathbb{Z},+)$ by Alice (in our implementation, all $r_i$ values are generated by a pseudorandom function). Let $Q_1$ be the program that takes as inputs $x,y, r_1$ (and empty state $s_0$), runs $P_1$ (as defined above) to get $s_1$ and then outputs $o_1 = s_1 + r_1$ {\em only to} Bob\footnote{While the description of our protocol here assumes that the underlying backend supports only one party receiving output, this is only a simplifying assumption, and we can easily modify our protocol in the case where both parties must receive the same output. To do so, we let $Q_1$ output $o_1 = s_1+r_1+t_1$ (where $t_1$ is random and chosen by Bob) and have both parties learn this. We can then appropriately modify the remaining steps as well.}. Alice's output from $Q_1$ is $r_1$. Next, every $Q_i$ ($2\leq i\leq k-1$) takes as inputs $x,y,r_{i-1},o_{i-1},r_i$, runs $P_i$ on inputs $x,y$ and state $o_{i-1}-r_{i-1}$ (where $-$ denotes subtraction in the ring $(\mathbb{Z},+)$) and then outputs $s_i+r_i$ only to Bob. Again, Alice's output from $P_i$ is $r_i$. The last program $Q_k$ takes inputs $x,y,r_{k-1},o_{k-1}$, runs $P_k$ on inputs $x,y$ and state $o_{k-1}-r_{k-1}$ and outputs $z$ to both parties.

@@

\begin{theorem}[Correctness and security of partitioning]
Let $P$ be a program in our source language with output $z$, that is decomposed into programs $Q_1||Q_2||\cdots ||Q_k$ (as defined in the partioning procedure above) and compiled into the protocol $\prot_1||\prot_2\cdots ||\prot_k$ that outputs $r_1||r_2||\cdots||z$ (to Alice) and $o_1||o_2||\cdots||z$ (to Bob), then $\prot$ securely realizes $P$.  
\end{theorem}

\noindent {\em Proof.} From Theorem \ref{theorem:security}, it follows that $\prot_i$ securely realizes $Q_i$ for every $1\leq i\leq k$. Hence, we know that the only information learnt by Alice is $r_1||r_2||\cdots||r_{k-1}||z$ and by Bob is $o_1||o_2||\cdots||o_{k-1}||z$. Since $r_i$ and $o_i$ ($1\leq i\leq k-1$) are individually uniformly random (in $(\mathbb{Z},+)$, the proof follows.

>>>>

We  describe ``secure code partitioning'' that allows us to execute {\it large} programs, i.e., programs with a large number of operations.
In more detail, let $P$ be a program in our source language that generates a circuit $\crct$. For a large enough $P$, the circuit $\crct$  can be larger than the memory size\footnote{In fact, there is an upper limit of $2^{32}-1$ gates for the circuit size in ABY but for most machines the memory limit is hit first.} and fail to execute. Partitioning enables us to
execute such programs via a source to source transformation that is oblivious to the underlying \mpc backend. Partitioning decomposes the program $P$ into a sequence of smaller \tool programs $Q_1||Q_2||\cdots||Q_k$ (defined below). We compile and execute each $Q_i$ sequentially, feeding the outputs of $Q_i$ as state information to $Q_{i+1}$. We prove that partioning is correct ($P$ and $Q_1||Q_2||\cdots||Q_k$ compute the same functionality) and secure (execution of $Q_1||Q_2||\cdots||Q_k$ does not reveal any more information than $P$). More details follow.

Let $P$ be a program that takes (secret) inputs $x$ from Alice and $y$ from Bob and produces an output $z$ to both parties. Let $P_1||P_2||\cdots||P_k$ be a sequence of programs such that the following holds: Define $s_0 = \bot$ (the public empty state). For all $1\leq i\leq k-1$, $P_i$ takes inputs $x, y$ and $s_{i-1}$ and outputs  state information $s_i$. Finally, $P_k$ takes inputs $x,y$ and $s_{k-1}$ to  output $z$. Each program $P_i$ ($1\leq i\leq k$) is required to be ``sufficiently'' small (as described later). It is possible to decompose any program $P$  into such $P_1||P_2||\cdots||P_k$. If \tool generates circuit $\crct_i$ from $P_i$, the parties can execute $\crct_1||\crct_2||\cdots||\crct_k$ sequentially (in a distributed setting)  to obtain $s_1,\cdots,s_{k-1},$ and finally output $z$. At the $i^{\textrm{\tiny{th}}}$ step, the parties only need to store information proportional to $x,y,s_{i-1}$ and $\crct_i$ (which is much smaller than $\crct$). However, this execution enables the parties to learn $s_i$ (for all $1\leq i\leq k-1$), which completely breaks the security.

To overcome this problem, we define a sequence of new programs $Q_i$ ($1\leq i\leq k$) as follows. Once again, define $s_0 = \bot$. Without loss of generality, let all $s_i$ be values in some additive ring $(\mathbb{Z},+)$ (e.g., the additive ring $(\mathbb{Z}_{2^{64}},+)$, i.e., the additive ring of integers modulo $2^{64}$). 
Let $r_1,\cdots,r_{k-1}$ be a sequence of random values sampled from the same ring $(\mathbb{Z},+)$ by Alice (in our implementation, all $r_i$ values are generated by a pseudorandom function). Let $Q_1$ be the program that takes as input $x,r_1$ from Alice and $y$ from Bob (and empty state $s_0$), and runs $P_1$ (as defined above) to compute $s_1$ and then outputs $o_1 = s_1 + r_1$ {\em only to} Bob\footnote{While the description of our protocol here assumes that the underlying backend supports only one party receiving output, this is only a simplifying assumption, and we can easily modify our protocol in the case where both parties must receive the same output. To do so, we modify $Q_1$ to output $o_1 = s_1+r_1+t_1$ to both parties (where $t_1$ is random and chosen by Bob). We can then appropriately modify the remaining steps as well.}. Alice's output from $Q_1$ is $r_1$. Next, every $Q_i$ ($2\leq i\leq k-1$) takes as inputs $x,r_{i-1},r_i$ from Alice and $y,o_{i-1}$ from Bob, runs $P_i$ on inputs $x,y$ and state $o_{i-1}-r_{i-1}$ (where $-$ denotes subtraction in the ring $(\mathbb{Z},+)$) and then outputs $s_i+r_i$ only to Bob. Again, Alice's output from $P_i$ is $r_i$. The last program $Q_k$ takes inputs $x,y,r_{k-1},o_{k-1}$, runs $P_k$ on inputs $x,y$ and state $o_{k-1}-r_{k-1}$ and outputs $z$ to both parties.

@@

\begin{theorem}[Correctness and security of partitioning]
Let $P$ be a program in our source language with output $z$, that is decomposed into programs $Q_1||Q_2||\cdots ||Q_k$ (as defined in the partioning procedure above) and compiled into the protocol $\prot = \prot_1||\prot_2\cdots ||\prot_k$ that outputs $r_1||r_2||\cdots||z$ (to Alice) and $o_1||o_2||\cdots||z$ (to Bob), then $\prot$ securely realizes $P$.  
\end{theorem}

\noindent {\em Proof.} From \theoremref{security}, it follows that $\prot_i$ securely realizes $Q_i$ for every $1\leq i\leq k$. Hence, we know that the only information learnt by Alice is $r_1||r_2||\cdots||r_{k-1}||z$ and by Bob is $o_1||o_2||\cdots||o_{k-1}||z$. Since $r_i$ and $o_i$ ($1\leq i\leq k-1$) are individually uniformly random (in $(\mathbb{Z},+)$, outputs received by the adversary can be easily simulated given the final output $z$.
